Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-09-22 paper/paper.Rmd
minor ms changes

author-note:
    "*These authors contributed equally and are listed alphabetically. **Carolyn Au, Juan Miguel Arias, Rhia Catapano, Eric Hermann, Marty Keil, Andrew Lampinen, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, and Jed Tan. Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."

@@

All study participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}.^[Note that of the `r nrow(d)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on Mechanical Turk.] All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."

@@

# Appendix: Project-By-Project Methods Addendum

@@

This paper found that when participants had the opportunity to save a file containing a list of target words before studying another file, they retained more information from the second study session. Our target for replication was Experiment 3, in which the effect was found to depend on the amount of information that was studied in the first file, with a greater effect for an eight-word list than a two-word list. The key statistical test we selected was the interaction in a 2x2 mixed-design ANOVA (save vs. no-save condition and two- vs. eight-word condition). The replication study failed to find evidence of the interaction, but ironically this was because we found evidence for a main effect of save condition: The authors' key manipulation succeeded for both load conditions. Perhaps even two words was sufficient to create interference for our online sample.

>>>>

author-note:
    "*These authors contributed equally and are listed alphabetically. **Carolyn Au, Juan Miguel Arias, Rhia Catapano, Eric Hermann, Martin Keil, Andrew Lampinen, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, and Jed Tan. Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."

@@

All study participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}.^[Note that of the `r nrow(d)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on Mechanical Turk.] Each sample was recruited independently (using the same account); most were All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."

@@

# SOM-R: Project-By-Project Methods Addendum

@@

This paper found that when participants had the opportunity to save a file containing a list of target words before studying another file, they retained more information from the second study session. Our target for replication was Experiment 3, in which the effect was found to depend on the amount of information that was studied in the first file, with a greater effect for an eight-word list than a two-word list. The key statistical test we selected was the interaction in a 2x2 mixed-design ANOVA (save vs. no-save condition and two- vs. eight-word condition). The replication study failed to find evidence of the interaction, but ironically this failure was because of a main effect of save condition: The authors' key manipulation succeeded for both load conditions. Perhaps even two words was sufficient to create interference for our online sample.
